Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-09 main.tex
Minor layout

\documentclass{article}

@@

\begin{figure}[ht!]
    \centering
    \subfigure[Nine allographs of the cursive ``h'', next to the reference]{
        \includegraphics[height=4.1cm]{h}
    }
    \subfigure[Same samples, normalized and projected in the eigen space spanned from the
        3 first eigenvectors: clusters arise, that actually match writing styles.]{
        \includegraphics[height=4.5cm]{eigenspace-uniformization}
    }

@@

@@

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\begin{tabular}{@{}lp{4.5cm}p{2.2cm}p{2.5cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Diego}     & Case-study, spanning over 4 weeks              & 1.5 hours $\times$ 4 weeks & 1                                     & 5          \\
{\it Haut-Lac}  & Pair (with turn-taking) interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Henry}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{Context, Study Design}
It was the first time we where trying a long-term interaction between a child
and the CoWriter robot. So the first aim of this study was to see if such an
interaction was simply possible. If we could create an environment to keep a child engaged
during one hour just in writing words with the robot.
The second question was focused on the content of the interaction. Our goal was
to figure out what extent the child would actually improve the robot's
writing.\\

Diego is a six years old child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplified by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

The experiment took one month. It was divided in four sessions of one hour, one session per week.
In order to justify to the child an activity where a robot wants to learn
handwriting, we decided to adduce a scenario. There where two Nao robots: a
blue one (Mimi) and an orange one (Clem). They where introduced to the child as
two hold friends. Mimi was left, and the two robots were corresponding by
handwritten mails. But Clem was beginning in writing and it needed the help of
Diego to write its responses to Mimi.\\

During the first session, Diego was just teaching single letters to the robot.
Gradually we increased the difficulty : the second session he was teaching
shirt words and in third session he was teaching long sentences. The last session was more like a test for Clem
: it had to prove to Mimi that it actually improved its handwriting thanks to
Diego.

@@

\subsubsection{Results}
Diego completely accepted our scenario and seriously played the game. At the
beginning he seemed not confident and intimidated.  But quickly, he gain in
confidence and complicity with the robot. Finally, he showed a real affinity, so
that he sent an handwritten mail to it some days after the last
session.\\

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided 154 letters as demonstration.\\

Diego felt he improved the robot's handwriting. To make clearly visible this
improvement, we printed the letter that the robot wrote during the third
session before and after the help of Diego~\ref{fig:stimuli}.

@@

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a complex scenario like the one for Diego was
no longer relevant with Henry. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

Before the experiment, Henry was working on writing numbers with the therapist.
Hence we decided to turn the CoWriter activity to teach numbers to the robot. Build on
existing iPad application actually used by occupational therapists (Dawson Toth's \emph{ABC's
Writer}), we designed an Android application for pre-test and post-test. It consisted in drawing
numbers following an helping pattern, that becomes more fine with levels in
order to increase difficulty~\ref{fig:abc-writer}.\\

@@

Since the robot was learning from scratch, each time Henry succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Henry quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. In total, over the three last sessions he provided 99
demonstrations of number shapes to the robot.

>>>>

%\documentclass[twocolumn]{article}
\documentclass{article}

@@

\begin{figure}[ht!]
    \centering
    \subfigure[Nine allographs of the cursive ``h'', next to the reference]{
        \includegraphics[width=0.4\columnwidth]{h}
    }
    \subfigure[Same samples, normalized and projected in the eigen space spanned from the
        3 first eigenvectors: clusters arise, that actually match writing styles.]{
        \includegraphics[width=0.4\columnwidth]{eigenspace-uniformization}
    }

@@

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\footnotesize
\begin{tabular}{@{}lp{4cm}p{2.2cm}p{1.8cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Diego}     & Case-study, spanning over 4 weeks              & 1.5 hours $\times$ 4 weeks & 1                                     & 5          \\
{\it Haut-Lac}  & Pair (with turn-taking) interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Henry}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

@@

\subsubsection{Context, Study Design}
The CoWriter activity needs a child engaged as interaction leader. In this
study we consider the problem of long-term interactions : is it possible to sustain this
engagement over several one-hour sessions ?\\

Diego is a six years old child with troubles in handwriting and a poor
self-esteem. Our goal was to figure out an environment in
order to make Diego sustaining engagement over four sessions of one hour, one
session per week. We decided to introduce an appealing scenario that justifyed to the child
the activity where a robot wants to learn handwriting. We used two Nao robots :
a blue one (called Mimi) and an orange one (called Clem). Mimi was away for a
mission,and the two robots had to communicate by mails. But they decided to do
it ``like humans", with handwritten messages. While Mimi was a good in
handwriting, Clem had strong difficulties and needed the help of Diego.\\

During the first session, Diego just teached single letters to the robot.
To chose a letter, he had to pick it in a set of magneted plastic letters, and to
show it to the robot. But the robot was not programmed to detect and recognize
it. A third person was entering the letter and was sending it to the
system with the computer. With following sessions we gradually increased the
difficulty : in the second session the child teached full words. To chose the
word, he had to assemble plastic letters to build it and to show it to the
robot. In the two last sessions, he teached long sentences. This time he just
had to say the sentence to the robot, and then the third person was using the
compurter to enter it. \\

We designed a special scenario for the last session : Mimi came back to the
laboratory. In front of Diego, Mimi said to Clem that it did not believe 
it realy improved its handwritting, and that the responses it recieved
was written by Diego. To prove that it actualy improved its writing,
it gave to Clem thirty minutes for a final training. After the training, it
asked to Clem to write some words. Finally, he admitted that Clem actually
improved its handwriting.

@@

\subsubsection{Results}
In all sessions, Diego was focused on the activity during forty minutes up to
one hour. In total, he provided 154 letters as demonstration.\\

Diego accepted our scenario and seriously played the game. At the
beginning he seemed not confident and intimidated.  But quickly, he gain in
confidence to play with the robot. He even showed real affective bonds : he
sent an handwritten mail to it some days after the last session.\\

As a technical result, we do not know if Diego improved his handwriting but he
likely conviced himself he was good enough at writing to help someone else (the
robot in that case). To show to Diego how much he improved the robot's
handwriting, we printed the letter that the robot wrote during the third session
before and after his help (Fig.~\ref{fig:stimuli}).

@@

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a scenario like the one we used for Diego was
no longer relevant with Henry. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

Before the experiment, Henry was working on writing numbers with the therapist.
Hence we decided to turn the CoWriter activity to teach numbers to the robot. Build on
existing iPad applications actually used by occupational therapists (Dawson Toth's \emph{ABC's
Writer}), we designed an Android application for pre-test and post-test. It consisted in drawing
numbers following an helping pattern, that becomes more fine with levels in
order to increase difficulty~\ref{fig:abc-writer}.\\

@@

Since the robot was learning from scratch, each time Henry succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Henry quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. Over the three last sessions he provided 99
demonstrations of number shapes to the robot.
